Beneficial arthropod habitat useage changes within-season: implications for pest control services in croplands

### 2020-10-02 manuscript/manuscript_outline.Rmd
Fixed table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
# library(kableExtra)
library(tidyverse)
library(mgcv)

@@

```{r rSquared, echo=FALSE, out.width='100%'}  
  r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>% 
  pivot_wider(names_from=model,values_from=r2comp) %>% 
  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>% 
  kable(.,caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
        col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
        digits=c(1,3,3,3,3),align='rllll',escape=FALSE, table.attr = "style='width:30%;'") 
```

@@

```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='', out.width='100%'}
  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(tidyverse)
library(mgcv)

@@

```{r rSquared, echo=FALSE, out.width='100%'}

r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>%
  pivot_wider(names_from=model,values_from=r2comp) %>%
  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
  kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
        col.names=linebreak(x=c('Term','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}'),align='l'),
        digits=c(1,3,3,3,3),align='rllll',escape=FALSE)
# test_data <- data.frame(Mean = runif(5, 3.71, 7.72),
#                         N = sample(57:59, 5, replace = TRUE),
#                         sd = c(1, rep(0, 4)),
#                         d = rep(1, 5),
#                         naod = sample(1:4, 5, replace = TRUE),
#                         a = sample(5:12, 5, replace = TRUE),
#                         sa = sample(37:44, 5, replace = TRUE))
# 
# kable(test_data,"latex" ,booktabs=T, align="c",
#       col.names=linebreak(c('Mean','\\textit{N}' ,'Strongly\n Disagree','Disagree','Neither Agree\n or Disagree','Agree','Strongly\n Agree')),
#       row.names = T,escape=F) %>%
#   row_spec(0,align = "c")

@@

```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='(ref:ParMoeSTCap)', out.width='100%'}
  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
```
